Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-05-10 AM+draft.tex
10 May, 18 Results section changes

\subsection{Simulation Study}

We were interested in answering two questions. 
First, is Eagle faster, computationally, than other competing implementations? Second, is Eagle better, statistically, at 
identifying the snp closest to the genes that are influencing a trait? To answer these questions, we conducted a large 
simulation study.

First, how does Eagle compare, computationally, to other competing implementations? Second, 
how accurate is Eagle for finding

\subsection{Computational Performance: run times and memory usage}

>>>>

\subsection{Simulation Study}
We performed a large simulation study where we sought to  answer two questions. 
First, how does Eagle compare, in terms of run time and memory usage, to 
competing implementations? Second, how well does Eagle find true associations (power) and avoid 
false associations (type 1 errors)? We generated data under five different scenarios; a study of size 150 individuals 
and 500 snp (150 x 5K),  350 individuals and 400000 snp (350 X 400K),  1500 individuals and 
50000 snp (1500 x 50K), 2000 individuals and 500000 snp (2000 x 500K), 4000 individuals and 
1500000 snp (4000 x 1.5M), and 10000 individuals and 1500000 snp (10000 x 1.5M).   
We chose these scenarios to mirror some of the different sized GWAS being performed in animals, plants, and humans.

For each scenario, we generated 100 replicates of data. A single replicate consists of snp data and quantitative trait data. 
To introduce some of the complexities of dealing with real genotypes into the study, we obtained the snp genotypes from 
the publicly available 1000 genome project, phase 3  \cite{10002010map}.  The quantitative trait data are generated 
by selecting randomly a set of snp loci, assigning allelic effects to these loci, and then aggregating these effects for 
each individual along with a random error.  
 The number of snp selected per replicate follows a Poisson distribution with mean 30. The sizes of the allelic effects 
 across the selected loci are equal.  A heritability of  50\% is assumed for the trait.

\subsection{Run times and memory usage}

Analyses were performed on a high end desktop computer. It had dual 8-core Xeon processors, and 128 Giggabytes of RAM. All implementations except, GEMMA, made use of distributed computing, either explicitly or implicitly through multi-threaded BLAS/LAPACK libraries.
